---
title: "PRS to cortical thick/vol/SA"
author: "Yuliya Zubak"
date: "11/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(emmeans)

setwd('/Users/Administrator/Desktop/R/YZ-20191122T154314Z-001/YZ') #move here so script works

```
#Loading
```{r}
HCP <- read.delim("HCP_sample_ref.txt", stringsAsFactors = FALSE)
genetic1 <- read.csv("scores_frontal_cortex_predicted_expression.csv",header=T,stringsAsFactors=F, row.names = 1)
imaging <- read.csv("unrestricted_amymiles_11_18_2019_13_10_13.csv",stringsAsFactors=FALSE)
clinical <- read.csv("HCP_behavioral_data.csv",header=T,stringsAsFactors=F)
family <- read.csv("HCP_subjects.csv",header=T,stringsAsFactors=F)

genetic <- merge(HCP[,c(4,5)],genetic1,by.x='SAMPLE_ID', by.y='IID')
colnames(genetic)[2] <- "SID"
```

```{r}
data <- merge(genetic[,c(2,3,4)],clinical[,c(1,2,10,11,204)],by.x='SID',by.y='Subject')
data <- merge(data,imaging,by.x='SID',by.y='Subject')

data <- merge(family[1], data[c(1,4,7)], by.x ='SID', by.y ='SID')


```
range(data[2])
[1] 22 36

 mean(as.numeric(unlist(data[2])))
[1] 28.79264

sd(unlist(data[2]))
[1] 3.704316

##Independent Variable (X)- Gender

```{r}
regressors <- data[,1:7]

sample <- subset(regressors,Race=='White')
sample <- subset(sample,Ethnicity=='Not Hispanic/Latino')
sample <- sample[,-c(5,6)]

```
##Moderating Variable (W)- Score

```{r}

volume <- data[,c(1,8,31:34,38,39,41,49:55)]
test.volume <- merge(sample,volume,by='SID')
thickness <- data[,c(1,8,71:138)]
test.thickness <- merge(sample,thickness,by='SID')
surfarea <- data[,c(1,8,139:206)]
test.surfarea <- merge(sample,surfarea,by='SID')

```

##COOKS 
if running cook's values, instead of ^ run cooks.rmd then this. CHECK EXCEL NAME
```{r}
test.volume <- test.volume.cd
test.thickness <-test.thickness.cd
test.surfarea <-test.surfarea.cd
```

##set factor
```{r}
test.volume$Gender <- as.factor(test.volume$Gender)
test.thickness$Gender <- as.factor(test.thickness$Gender)
test.surfarea$Gender <- as.factor(test.surfarea$Gender)

test.volume <- within(test.volume, Gender <- relevel(Gender, ref = 'M'))
test.thickness <- within(test.thickness, Gender <- relevel(Gender, ref = 'M'))
test.surfarea <- within(test.surfarea, Gender <- relevel(Gender, ref = 'M'))
```
##Dependant Variable (Y)- Thickness, SA, Volume

Y = b0+b2W+(b1 +b3W)X
lm (X, Y)
lm (Gender, Vol/thickness etc)
lm (dependant ~ interacting variable)

#MALE SCORE x MALE DATA (M=0)
##volume
```{r}
volume = matrix(,ncol = 7)
colnames(volume) <- c("ROI", "tval.maleWeighted", "pval.maleWeighted", "fdr.maleWeighted", "tval.maleWeighed*Gender", "pval.maleWeighted*Gender", "fdr.maleWeighted*Gender")

for(i in names(test.volume[,7:20])){
  var <- paste(i)
  glm <- summary(glm(test.volume[[i]]~test.volume$male.weighted*test.volume$Gender+test.volume$Age_in_Yrs+test.volume$FS_IntraCranial_Vol))
  tval.maleunweighted <- glm$coefficients[2,3]
  tval.male.gender <- glm$coefficients[6,3]
  pval.maleunweighted <- glm$coefficients[2,4]
  pval.male.gender <- glm$coefficients[6,4]
  fdr.maleunweighted <- c(0)
  fdr.male.gender <- c(0)
  volume <- rbind(
    volume,
    c(var,round(tval.maleunweighted,3),
      pval.maleunweighted,
      fdr.maleunweighted, 
      round(tval.male.gender, 3), 
      pval.male.gender, 
      fdr.male.gender))}

volume <-as.data.frame(volume[2:15,1:7])
fdr.w.volume <- p.adjust((as.numeric(as.character(volume[,3]))),method='fdr')
fdr.wm.volume <- p.adjust((as.numeric(as.character(volume[,6]))),method='fdr')
volume$fdr.maleWeighted <- round (fdr.w.volume,3)
volume$`fdr.maleWeighted*Gender` <- round (fdr.wm.volume,3)


m.s.m.d.volume <- volume
```


##thickness
```{r}
thickness = matrix(,ncol = 7)
colnames(thickness) <- c("ROI", "tval.maleWeighted", "pval.maleWeighted", "fdr.maleWeighted", "tval.maleWeighed*Gender", "pval.maleWeighted*Gender", "fdr.maleWeighted*Gender")

for(i in names(test.thickness[7:74])){
  var <- paste(i)
  glm <- summary(glm(test.thickness[[i]]~test.thickness$male.weighted*test.thickness$Gender+test.thickness$Age_in_Yrs))
  tval.maleunweighted <- glm$coefficients[2,3] #test.thickness$male.weighted
  tval.male.gender <- glm$coefficients[5,3] #test.thickness$male.weighted:test.thickness$GenderF
  pval.maleunweighted <- glm$coefficients[2,4]
  pval.male.gender <- glm$coefficients[5,4]
  fdr.maleunweighted <- round(p.adjust(pval.maleunweighted,method='fdr'),3)
  fdr.male.gender <- round(p.adjust(pval.male.gender,method='fdr'),3)
   thickness <- rbind(
    thickness,
    c(var,round(tval.maleunweighted,3),
      pval.maleunweighted,
      fdr.maleunweighted, 
      round(tval.male.gender, 3), 
      pval.male.gender, 
      fdr.male.gender))}

thickness <-as.data.frame(thickness[3:69,1:7])
fdr.w.thickness <- p.adjust((as.numeric(as.character(thickness[,3]))),method='fdr')
fdr.wm.thickness <- p.adjust((as.numeric(as.character(thickness[,6]))),method='fdr')
thickness$fdr.maleWeighted <- round (fdr.w.thickness,3)
thickness$`fdr.maleWeighted*Gender` <- round (fdr.wm.thickness,3)


m.s.m.d.thickness <- thickness
```

##surface area
```{r}

surfarea = matrix(,ncol = 7)
colnames(surfarea) <- c("ROI", "tval.maleWeighted", "pval.maleWeighted", "fdr.maleWeighted", "tval.maleWeighed*Gender", "pval.maleWeighted*Gender", "fdr.maleWeighted*Gender")

for(i in names(test.surfarea[7:74])){
  var <- paste(i)
  glm <- summary(glm(test.surfarea[[i]]~test.surfarea$male.weighted*test.surfarea$Gender+test.surfarea$Age_in_Yrs+test.surfarea$FS_IntraCranial_Vol))
  tval.maleunweighted <- glm$coefficients[2,3]
  tval.male.gender <- glm$coefficients[6,3]
  pval.maleunweighted <- glm$coefficients[2,4]
  pval.male.gender <- glm$coefficients[6,4]
  fdr.maleunweighted <- round(p.adjust(pval.maleunweighted,method='fdr'),3)
  fdr.male.gender <- round(p.adjust(pval.male.gender,method='fdr'),3)
  surfarea <- rbind(
    surfarea,
    c(var,round(tval.maleunweighted,3),
      pval.maleunweighted,
      fdr.maleunweighted, 
      round(tval.male.gender, 3), 
      pval.male.gender, 
      fdr.male.gender))}

surfarea <-as.data.frame(surfarea[2:69,1:7])
fdr.w.surfarea <- p.adjust((as.numeric(as.character(surfarea[,3]))),method='fdr')
fdr.wm.surfarea <- p.adjust((as.numeric(as.character(surfarea[,6]))),method='fdr')
surfarea$fdr.maleWeighted <- round (fdr.w.surfarea,3)
surfarea$`fdr.maleWeighted*Gender` <- round (fdr.wm.surfarea,3)


m.s.m.d.surfarea <- surfarea
```

##write to excel
add CookDist
```{r}
library(xlsx) #issues with java not being found -> install 64 bit verison of java and set home for java
write.xlsx(m.s.m.d.thickness, file="CooksDistMaleScoreMaleData.xlsx", sheetName="thickness", row.names=FALSE)
write.xlsx(m.s.m.d.volume, file="CooksDistMaleScoreMaleData.xlsx", sheetName="volume", append=TRUE, row.names=FALSE)
write.xlsx(m.s.m.d.surfarea, file="CooksDistMaleScoreMaleData.xlsx", sheetName="surfarea", append=TRUE, row.names=FALSE)
```


#FEMALE SCORE x MALE DATA (M=0)
##volume
```{r}
volume = matrix(,ncol = 7)
colnames(volume) <- c("ROI", "tval.femaleWeighted", "pval.femaleWeighted", "fdr.femaleWeighted", "tval.femaleWeighed*Gender", "pval.femaleWeighted*Gender", "fdr.femaleWeighted*Gender")


for(i in names(test.volume[,7:20])){
  var <- paste(i)
  glm <- summary(glm(test.volume[[i]]~test.volume$female.weighted*test.volume$Gender+test.volume$Age_in_Yrs+test.volume$FS_IntraCranial_Vol))
  tval.maleunweighted <- glm$coefficients[2,3]
  tval.male.gender <- glm$coefficients[6,3]
  pval.maleunweighted <- glm$coefficients[2,4]
  pval.male.gender <- glm$coefficients[6,4]
  fdr.maleunweighted <- round(p.adjust(pval.maleunweighted,method='fdr'),3)
  volume <- rbind(
    volume,
    c(var,round(tval.maleunweighted,3),
      pval.maleunweighted,
      fdr.maleunweighted, 
      round(tval.male.gender, 3), 
      pval.male.gender, 
      fdr.male.gender))}

volume <-as.data.frame(volume[2:15,1:7])
fdr.w.volume <- p.adjust((as.numeric(as.character(volume[,3]))),method='fdr')
fdr.wm.volume <- p.adjust((as.numeric(as.character(volume[,6]))),method='fdr')
volume$fdr.femaleWeighted <- round (fdr.w.volume,3)
volume$`fdr.femaleWeighted*Gender` <- round (fdr.wm.volume,3)


f.s.m.d.volume <- volume
```
##thickness
```{r}
thickness = matrix(,ncol = 7)
colnames(thickness) <- c("ROI", "tval.femaleWeighted", "pval.femaleWeighted", "fdr.femaleWeighted", "tval.femaleWeighed*Gender", "pval.femaleWeighted*Gender", "fdr.femaleWeighted*Gender")


for(i in names(test.thickness[7:74])){
  var <- paste(i)
  glm <- summary(glm(test.thickness[[i]]~test.thickness$female.weighted*test.thickness$Gender+test.thickness$Age_in_Yrs))
  tval.maleunweighted <- glm$coefficients[2,3]
  tval.male.gender <- glm$coefficients[5,3]
  pval.maleunweighted <- glm$coefficients[2,4]
  pval.male.gender <- glm$coefficients[5,4]
  fdr.maleunweighted <- round(p.adjust(pval.maleunweighted,method='fdr'),3)
  fdr.male.gender <- round(p.adjust(pval.male.gender,method='fdr'),3)
  thickness <- rbind(
    thickness,
    c(var,round(tval.maleunweighted,3),
      pval.maleunweighted,
      fdr.maleunweighted, 
      round(tval.male.gender, 3), 
      pval.male.gender, 
      fdr.male.gender))}

thickness <-as.data.frame(thickness[3:69,1:7])
fdr.w.thickness <- p.adjust((as.numeric(as.character(thickness[,3]))),method='fdr')
fdr.wm.thickness <- p.adjust((as.numeric(as.character(thickness[,6]))),method='fdr')
thickness$fdr.femaleWeighted <- round (fdr.w.thickness,3)
thickness$`fdr.femaleWeighted*Gender` <- round (fdr.wm.thickness,3)


f.s.m.d.thickness <- thickness
```
##surfarea
```{r}

surfarea = matrix(,ncol = 7)
colnames(surfarea) <-c("ROI", "tval.femaleWeighted", "pval.femaleWeighted", "fdr.femaleWeighted", "tval.femaleWeighed*Gender", "pval.femaleWeighted*Gender", "fdr.femaleWeighted*Gender")

for(i in names(test.surfarea[7:74])){
  var <- paste(i)
  glm <- summary(glm(test.surfarea[[i]]~test.surfarea$female.weighted*test.surfarea$Gender+test.surfarea$Age_in_Yrs+test.surfarea$FS_IntraCranial_Vol))
  tval.maleunweighted <- glm$coefficients[2,3]
  tval.male.gender <- glm$coefficients[6,3]
  pval.maleunweighted <- glm$coefficients[2,4]
  pval.male.gender <- glm$coefficients[6,4]
  fdr.maleunweighted <- round(p.adjust(pval.maleunweighted,method='fdr'),3)
  fdr.male.gender <- round(p.adjust(pval.male.gender,method='fdr'),3)
   surfarea <- rbind(
    surfarea,
    c(var,round(tval.maleunweighted,3),
      pval.maleunweighted,
      fdr.maleunweighted, 
      round(tval.male.gender, 3), 
      pval.male.gender, 
      fdr.male.gender))}

surfarea <-as.data.frame(surfarea[2:69,1:7])
fdr.w.surfarea <- p.adjust((as.numeric(as.character(surfarea[,3]))),method='fdr')
fdr.wm.surfarea <- p.adjust((as.numeric(as.character(surfarea[,6]))),method='fdr')
surfarea$fdr.femaleWeighted <- round (fdr.w.surfarea,3)
surfarea$`fdr.femaleWeighted*Gender` <- round (fdr.wm.surfarea,3)


f.s.m.d.surfarea <- surfarea
```
##write to excel
```{r}
library(xlsx)
write.xlsx(f.s.m.d.thickness, file="CooksDistFemaleScoreMaleData.xlsx", sheetName="thickness", row.names=FALSE)
write.xlsx(f.s.m.d.volume, file="CooksDistFemaleScoreMaleData.xlsx", sheetName="volume", append=TRUE, row.names=FALSE)
write.xlsx(f.s.m.d.surfarea, file="CooksDistFemaleScoreMaleData.xlsx", sheetName="surfarea", append=TRUE, row.names=FALSE)
```

#MALE SCORE x FEMALE DATA (F=0)
##factor
```{r}
test.volume <- within(test.volume, Gender <- relevel(Gender, ref = 'F'))
test.thickness <- within(test.thickness, Gender <- relevel(Gender, ref = 'F'))
test.surfarea <- within(test.surfarea, Gender <- relevel(Gender, ref = 'F'))
```

##volume
```{r}
volume = matrix(,ncol = 7)
colnames(volume) <- c("ROI", "tval.maleWeighted", "pval.maleWeighted", "fdr.maleWeighted", "tval.maleWeighed*Gender", "pval.maleWeighted*Gender", "fdr.maleWeighted*Gender")

for(i in names(test.volume[,7:20])){
  var <- paste(i)
  glm <- summary(glm(test.volume[[i]]~test.volume$male.weighted*test.volume$Gender+test.volume$Age_in_Yrs+test.volume$FS_IntraCranial_Vol))
  tval.maleunweighted <- glm$coefficients[2,3]
  tval.male.gender <- glm$coefficients[6,3]
  pval.maleunweighted <- glm$coefficients[2,4]
  pval.male.gender <- glm$coefficients[6,4]
  fdr.maleunweighted <- round(p.adjust(pval.maleunweighted,method='fdr'),3)
  fdr.male.gender <- round(p.adjust(pval.male.gender,method='fdr'),3)
  volume <- rbind(
    volume,
    c(var,round(tval.maleunweighted,3),
      pval.maleunweighted,
      fdr.maleunweighted, 
      round(tval.male.gender, 3), 
      pval.male.gender, 
      fdr.male.gender))}

volume <-as.data.frame(volume[2:15,1:7])
fdr.w.volume <- p.adjust((as.numeric(as.character(volume[,3]))),method='fdr')
fdr.wm.volume <- p.adjust((as.numeric(as.character(volume[,6]))),method='fdr')
volume$fdr.maleWeighted <- round (fdr.w.volume,3)
volume$`fdr.maleWeighted*Gender` <- round (fdr.wm.volume,3)


m.s.f.d.volume <- volume
```
##thickness
```{r}
thickness = matrix(,ncol = 7)
colnames(thickness) <- c("ROI", "tval.maleWeighted", "pval.maleWeighted", "fdr.maleWeighted", "tval.maleWeighed*Gender", "pval.maleWeighted*Gender", "fdr.maleWeighted*Gender")


for(i in names(test.thickness[7:74])){
  var <- paste(i)
  glm <- summary(glm(test.thickness[[i]]~test.thickness$male.weighted*test.thickness$Gender+test.thickness$Age_in_Yrs))
  tval.maleunweighted <- glm$coefficients[2,3]
  tval.male.gender <- glm$coefficients[5,3]
  pval.maleunweighted <- glm$coefficients[2,4]
  pval.male.gender <- glm$coefficients[5,4]
  fdr.maleunweighted <- round(p.adjust(pval.maleunweighted,method='fdr'),3)
  fdr.male.gender <- round(p.adjust(pval.male.gender,method='fdr'),3)
   thickness <- rbind(
    thickness,
    c(var,round(tval.maleunweighted,3),
      pval.maleunweighted,
      fdr.maleunweighted, 
      round(tval.male.gender, 3), 
      pval.male.gender, 
      fdr.male.gender))}

thickness <-as.data.frame(thickness[3:69,1:7])
fdr.w.thickness <- p.adjust((as.numeric(as.character(thickness[,3]))),method='fdr')
fdr.wm.thickness <- p.adjust((as.numeric(as.character(thickness[,6]))),method='fdr')
thickness$fdr.maleWeighted <- round (fdr.w.thickness,3)
thickness$`fdr.maleWeighted*Gender` <- round (fdr.wm.thickness,3)


m.s.f.d.thickness <- thickness
```
##surfarea
```{r}

surfarea = matrix(,ncol = 7)
colnames(surfarea) <- c("ROI", "tval.maleWeighted", "pval.maleWeighted", "fdr.maleWeighted", "tval.maleWeighed*Gender", "pval.maleWeighted*Gender", "fdr.maleWeighted*Gender")


for(i in names(test.surfarea[7:74])){
  var <- paste(i)
  glm <- summary(glm(test.surfarea[[i]]~test.surfarea$male.weighted*test.surfarea$Gender+test.surfarea$Age_in_Yrs+test.surfarea$FS_IntraCranial_Vol))
  tval.maleunweighted <- glm$coefficients[2,3]
  tval.male.gender <- glm$coefficients[6,3]
  pval.maleunweighted <- glm$coefficients[2,4]
  pval.male.gender <- glm$coefficients[6,4]
  fdr.maleunweighted <- round(p.adjust(pval.maleunweighted,method='fdr'),3)
  fdr.male.gender <- round(p.adjust(pval.male.gender,method='fdr'),3)
  surfarea <- rbind(
    surfarea,
    c(var,round(tval.maleunweighted,3),
      pval.maleunweighted,
      fdr.maleunweighted, 
      round(tval.male.gender, 3), 
      pval.male.gender, 
      fdr.male.gender))}

surfarea <-as.data.frame(surfarea[2:69,1:7])
fdr.w.surfarea <- p.adjust((as.numeric(as.character(surfarea[,3]))),method='fdr')
fdr.wm.surfarea <- p.adjust((as.numeric(as.character(surfarea[,6]))),method='fdr')
surfarea$fdr.maleWeighted <- round (fdr.w.surfarea,3)
surfarea$`fdr.maleWeighted*Gender` <- round (fdr.wm.surfarea,3)


m.s.f.d.surfarea <- surfarea
```
##write to excel
```{r}
library(xlsx) 
write.xlsx(m.s.f.d.thickness, file="CooksDistMaleScoreFemaleData.xlsx", sheetName="thickness", row.names=FALSE)
write.xlsx(m.s.f.d.volume, file="CooksDistMaleScoreFemaleData.xlsx", sheetName="volume", append=TRUE, row.names=FALSE)
write.xlsx(m.s.f.d.surfarea, file="CooksDistMaleScoreFemaleData.xlsx", sheetName="surfarea", append=TRUE, row.names=FALSE)
```


#FEMALE SCORE x FEMALE DATA (F=0) 
##volume
```{r}
volume = matrix(,ncol = 7)
colnames(volume) <- c("ROI", "tval.femaleWeighted", "pval.femaleWeighted", "fdr.femaleWeighted", "tval.femaleWeighed*Gender", "pval.femaleWeighted*Gender", "fdr.femaleWeighted*Gender")


for(i in names(test.volume[,7:20])){
  var <- paste(i)
  glm <- summary(glm(test.volume[[i]]~test.volume$female.weighted*test.volume$Gender+test.volume$Age_in_Yrs+test.volume$FS_IntraCranial_Vol))
  tval.maleunweighted <- glm$coefficients[2,3]
  tval.male.gender <- glm$coefficients[6,3]
  pval.maleunweighted <- glm$coefficients[2,4]
  pval.male.gender <- glm$coefficients[6,4]
  fdr.maleunweighted <- round(p.adjust(pval.maleunweighted,method='fdr'),3)
  fdr.male.gender <- round(p.adjust(pval.male.gender,method='fdr'),3)
  volume <- rbind(
    volume,
    c(var,round(tval.maleunweighted,3),
      pval.maleunweighted,
      fdr.maleunweighted, 
      round(tval.male.gender, 3), 
      pval.male.gender, 
      fdr.male.gender))}

volume <-as.data.frame(volume[2:15,1:7])
fdr.w.volume <- p.adjust((as.numeric(as.character(volume[,3]))),method='fdr')
fdr.wm.volume <- p.adjust((as.numeric(as.character(volume[,6]))),method='fdr')
volume$fdr.femaleWeighted <- round (fdr.w.volume,3)
volume$`fdr.femaleWeighted*Gender` <- round (fdr.wm.volume,3)


f.s.f.d.volume <- volume
```
##thickness
```{r}
thickness = matrix(,ncol = 7)
colnames(thickness) <-c("ROI", "tval.femaleWeighted", "pval.femaleWeighted", "fdr.femaleWeighted", "tval.femaleWeighed*Gender", "pval.femaleWeighted*Gender", "fdr.femaleWeighted*Gender")


for(i in names(test.thickness[7:74])){
  var <- paste(i)
  glm <- summary(glm(test.thickness[[i]]~test.thickness$female.weighted*test.thickness$Gender+test.thickness$Age_in_Yrs))
  tval.maleunweighted <- glm$coefficients[2,3]
  tval.male.gender <- glm$coefficients[5,3]
  pval.maleunweighted <- glm$coefficients[2,4]
  pval.male.gender <- glm$coefficients[5,4]
  fdr.maleunweighted <- round(p.adjust(pval.maleunweighted,method='fdr'),3)
  fdr.male.gender <- round(p.adjust(pval.male.gender,method='fdr'),3)
 thickness <- rbind(
    thickness,
    c(var,round(tval.maleunweighted,3),
      pval.maleunweighted,
      fdr.maleunweighted, 
      round(tval.male.gender, 3), 
      pval.male.gender, 
      fdr.male.gender))}

thickness <-as.data.frame(thickness[3:69,1:7])
fdr.w.thickness <- p.adjust((as.numeric(as.character(thickness[,3]))),method='fdr')
fdr.wm.thickness <- p.adjust((as.numeric(as.character(thickness[,6]))),method='fdr')
thickness$fdr.femaleWeighted <- round (fdr.w.thickness,3)
thickness$`fdr.femaleWeighted*Gender` <- round (fdr.wm.thickness,3)


f.s.f.d.thickness <- thickness
```
##surfarea
```{r}

surfarea = matrix(,ncol = 7)
colnames(surfarea) <- c("ROI", "tval.femaleWeighted", "pval.femaleWeighted", "fdr.femaleWeighted", "tval.femaleWeighed*Gender", "pval.femaleWeighted*Gender", "fdr.femaleWeighted*Gender")

for(i in names(test.surfarea[7:74])){
  var <- paste(i)
  glm <- summary(glm(test.surfarea[[i]]~test.surfarea$female.weighted*test.surfarea$Gender+test.surfarea$Age_in_Yrs+test.surfarea$FS_IntraCranial_Vol))
  tval.maleunweighted <- glm$coefficients[2,3]
  tval.male.gender <- glm$coefficients[6,3]
  pval.maleunweighted <- glm$coefficients[2,4]
  pval.male.gender <- glm$coefficients[6,4]
  fdr.maleunweighted <- round(p.adjust(pval.maleunweighted,method='fdr'),3)
  fdr.male.gender <- round(p.adjust(pval.male.gender,method='fdr'),3)
   surfarea <- rbind(
    surfarea,
    c(var,round(tval.maleunweighted,3),
      pval.maleunweighted,
      fdr.maleunweighted, 
      round(tval.male.gender, 3), 
      pval.male.gender, 
      fdr.male.gender))}

surfarea <-as.data.frame(surfarea[3:69,1:7])
fdr.w.surfarea <- p.adjust((as.numeric(as.character(surfarea[,3]))),method='fdr')
fdr.wm.surfarea <- p.adjust((as.numeric(as.character(surfarea[,6]))),method='fdr')
surfarea$fdr.femaleWeighted <- round (fdr.w.surfarea,3)
surfarea$`fdr.femaleWeighted*Gender` <- round (fdr.wm.surfarea,3)


f.s.f.d.surfarea <- surfarea
```
##write to excel
```{r}
library(xlsx) 
write.xlsx(f.s.f.d.thickness, file="CooksDistFemaleScoreFemaleData.xlsx", sheetName="thickness", row.names=FALSE)
write.xlsx(f.s.f.d.volume, file="CooksDistFemaleScoreFemaleData.xlsx", sheetName="volume", append=TRUE, row.names=FALSE)
write.xlsx(f.s.f.d.surfarea, file="CooksDistFemaleScoreFemaleData.xlsx", sheetName="surfarea", append=TRUE, row.names=FALSE)
```

#ggplot, dplyr
I use this to generate any one graph
```{r}
library(dplyr)
library(ggplot2)

test.thickness.cd.subset <- subset(test.thickness.cd,Gender=='F')
p <- ggplot(test.thickness.cd.subset, aes(x=female.weighted, y=FS_L_Parsorbitalis_Thck))+geom_boxplot(outlier.color="red")+ylim(2.5,3.6)
p
qplot(x= female.weighted, y=FS_L_Parsorbitalis_Thck, data= test.thickness.cd.subset)+geom_smooth(method = "glm")

```